---
title: "SALURhelper"
format: gfm
---

## Overview

The *Salud Urbana en America Latina* (SALURBAL) research project and it's successor, SALURBAL-Climate, are focused understanding health in urban Latin America. Many of these papers use similar statistical methods. This package provides a centralized location for common helper functions used in such research.

## Installation

```{r}
#| eval: false

devtools::install_github("SALURBAL-Climate/SALURhelper")
library(SALURhelper)
```

## Usage

To get the QAIC of a quasi-Poisson model, use the `QAIC` function on the model output.

```{r}
fit <- glm(hp ~ mpg + disp + wt, family = "quasipoisson", data = mtcars)
stats::AIC(fit)
SALURhelper::QAIC(fit)
```

## How to Contribute

This package is meant to serve SALURBAL researchers, and we want to incorporate any feedback to make the package better.

- If you have ideas for functions that you would like to add to `SALURhelper`, please file an [issue](https://github.com/SALURBAL-Climate/SALURhelper/issues). 
- If you encounter and bugs, or suspect the code is not functioning properly, please file an [issue](https://github.com/SALURBAL-Climate/SALURhelper/issues) with a [minimum reproducible example](https://stackoverflow.com/help/minimal-reproducible-example).
